Ethereum: A Secure Decentralised Generalised Transaction Ledger \\ {\smaller \textbf{Proof-of-Concept V}}

### 2014-05-21 Paper.tex
byte arrays are not arb length.

\begin{description}
\item[nonce] A scalar value equal to the number of transactions sent from this address, or, in the case of contract accounts, the number of contract-creations made by this account. For account of address $a$ in state $\boldsymbol{\sigma}$, this would be formally denoted $\boldsymbol{\sigma}[a]_n$.
\item[balance] A scalar value equal to the number of Wei owned by this address. Formally denoted $\boldsymbol{\sigma}[a]_b$.
\item[stateRoot] A 256-bit hash of the root node of a trie structure that encodes the storage contents of the contract, itself a simple mapping from byte arrays of size 32 to arbitrary length byte arrays. The hash is formally denoted $\boldsymbol{\sigma}[a]_s$. Since I typically wish to refer not to the trie's root hash but to the underlying set of key/value pairs stored within, I define a convenient equivalence $\texttt{\small TRIE}(\boldsymbol{\sigma}[a]_\mathbf{s}) \equiv \boldsymbol{\sigma}[a]_s$. It shall be understood that $\boldsymbol{\sigma}[a]_\mathbf{s}$ is not a `physical' member of the account and does not contribute to its later serialisation.
\item[codeHash] The hash of the EVM code of this contract---this is the code that gets executed should this address receive a message call; it is immutable and thus, unlike all other fields, cannot be changed after construction. All such code fragments are contained in the state database under their corresponding hashes for later retrieval. This hash is formally denoted $\boldsymbol{\sigma}[a]_c$, and thus the code may be denoted as $\mathbf{b}$, given that $\texttt{\small SHA3}(\mathbf{b}) = \boldsymbol{\sigma}[a]_c$.
\end{description}

>>>>

\begin{description}
\item[nonce] A scalar value equal to the number of transactions sent from this address, or, in the case of contract accounts, the number of contract-creations made by this account. For account of address $a$ in state $\boldsymbol{\sigma}$, this would be formally denoted $\boldsymbol{\sigma}[a]_n$.
\item[balance] A scalar value equal to the number of Wei owned by this address. Formally denoted $\boldsymbol{\sigma}[a]_b$.
\item[stateRoot] A 256-bit hash of the root node of a trie structure that encodes the storage contents of the contract, itself a simple mapping between byte arrays of size 32. The hash is formally denoted $\boldsymbol{\sigma}[a]_s$. Since I typically wish to refer not to the trie's root hash but to the underlying set of key/value pairs stored within, I define a convenient equivalence $\texttt{\small TRIE}(\boldsymbol{\sigma}[a]_\mathbf{s}) \equiv \boldsymbol{\sigma}[a]_s$. It shall be understood that $\boldsymbol{\sigma}[a]_\mathbf{s}$ is not a `physical' member of the account and does not contribute to its later serialisation.
\item[codeHash] The hash of the EVM code of this contract---this is the code that gets executed should this address receive a message call; it is immutable and thus, unlike all other fields, cannot be changed after construction. All such code fragments are contained in the state database under their corresponding hashes for later retrieval. This hash is formally denoted $\boldsymbol{\sigma}[a]_c$, and thus the code may be denoted as $\mathbf{b}$, given that $\texttt{\small SHA3}(\mathbf{b}) = \boldsymbol{\sigma}[a]_c$.
\end{description}
